\documentclass[a4paper,10pt]{article}
\usepackage[left=0.6in, right=0.6in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem, hyperref, fontawesome, titlesec}
\usepackage{helvet, xcolor, fancyhdr}
\usepackage{fontspec}

\renewcommand{\familydefault}{\rmdefault} % Ensure proper font support
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\pagestyle{empty}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\newcommand{\namefont}{\fontsize{22}{24}\selectfont}
\newcommand{\locationfont}{\fontsize{12}{14}\selectfont}

\begin{document}

\begin{center}
    {\namefont \textbf{SAKET SATYAM}} \\ 
    {\locationfont Bhubaneswar, Odisha, India} \\ 
    \vspace{2pt}
    \faPhone~ +91 7764009596 \textbullet~
    \faEnvelope~ \href{mailto:satyamsaket09876@gmail.com}{satyamsaket09876@gmail.com} \textbullet~
    \faLinkedin~ \href{https://www.linkedin.com/in/saket-satyam}{linkedin}
\end{center}

\section*{Summary}
Passionate and motivated third-year B.Tech Computer Science Engineering student at KIIT University, specializing in full-stack development. Strong foundation in programming, web development, and cloud technologies. Quick learner with excellent problem-solving skills, eager to contribute to innovative projects.

\section*{Education}
\textbf{Kalinga Institute of Industrial Technology (KIIT), Bhubaneswar, Odisha} \hfill \textbf{2022 -- 2026} \\
B.Tech in Computer Science and Engineering (CGPA: 7.9)

\textbf{National Public Welfare Inter College} \hfill \textbf{2020 -- 2021} \\
Class 12 (Intermediate) -- 75\%

\textbf{DAV Centenary Public School} \hfill \textbf{2018 -- 2019} \\
Class 10 (Matriculation) -- 93\%

\section*{Technical Skills}
\textbf{Programming Languages:} C/C++, Python, Java, JavaScript \\
\textbf{Web Technologies:} HTML, CSS, Bootstrap, Tailwind CSS \\
\textbf{Cloud \slash DevOps:} AWS, Docker \\
\textbf{Frameworks \slash Libraries:} React.js, Node.js,REST APIs \\
\textbf{Developer Tools:} Git, VS Code, IntelliJ, Postman, Eclipse \\
\textbf{Core CS Concepts:} Data Structures \& Algorithms, OOP, OS, Computer Networks \\
\textbf{Soft Skills:} Problem Solving, Time Management, Team Collaboration

\section*{Internship}
\textbf{OctaNet Services Pvt Ltd.} \hfill \textbf{May 2024 -- July 2024} \\
\textit{Full Stack Development Intern}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed and deployed a user-friendly Money Tracker application.
    \item Designed and optimized database schemas using MongoDB.
    \item Created back-end services with Node.js for data manipulation and business logic.
\end{itemize}

\section*{Projects}
\textbf{Learning Management System (LMS)} \hfill \textbf{February 2025} \\
\textit{Technologies: MERN Stack, Cloudinary, Multer, API Integration, MongoDB}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed a responsive and user-friendly interface for seamless user experience.
    \item Implemented JWT authentication for secure user access.
    \item Reduced load time and ensured smooth performance across devices.
\end{itemize}
\textbf{E-Commerce Website} \hfill \textbf{March 2024} \\
\textit{Technologies: HTML,JavaScript,Next.js,MongoDB,React,CSS}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed a responsive and user-friendly interface for seamless shopping.
    \item Implemented real-time inventory management and authentication security.
    \item Optimized website performance for better user experience across devices.
\end{itemize}

\end{document}
